Calculate cloud cover of scenes

### 2019-06-18 analysis/eda.Rmd
move figure
fix git

```{r eda-1}
intro <- introduce(vi_data)
knitr::kable(intro)
```

@@

```{r eda-5}
intro <- introduce(nri_data)
knitr::kable(intro)
```

@@

```{r eda-8}
intro <- introduce(bands_data)
knitr::kable(intro)
```

@@

```{r echo = FALSE}
file_move(list.files(here("docs/figure/eda.Rmd/"), 
                     pattern = "defoliation-distribution-plot", 
                     full.names = TRUE),
          here("code/98-paper/journal/"))
```

>>>>

```{r eda-1}
intro <- introduce(vi_data)

intro_df <- data.frame(
  "Name" = c("Rows", "Columns",
             "Discrete columns", "Continuous columns", "All missing columns",
             "Missing observations", "Complete Rows",
             "Total observations"),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-5}
intro <- introduce(nri_data)
intro_df <- data.frame(
  "Name" = c("Rows", "Columns",
             "Discrete columns", "Continuous columns", "All missing columns",
             "Missing observations", "Complete Rows",
             "Total observations",
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-8}
intro <- introduce(bands_data)
intro_df <- data.frame(
  "Name" = c("Rows", "Columns",
             "Discrete columns", "Continuous columns", "All missing columns",
             "Missing observations", "Complete Rows",
             "Total observations",
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r echo = FALSE}
file_move("docs/figure/eda.Rmd/defoliation-distribution-plot-1.pdf",
          "code/98-paper/journal/")
```

### 2019-06-18 analysis/test/cloud-cover.Rmd
fix git

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = 'analysis/rmd/')
knitr::opts_chunk$set(fig.retina = 3, fig.align = 'center', fig.width = 6.93, 
                      fig.height = 6.13, out.width = "100%")

@@

```{r}
records %<>% split(records$beginposition)

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = 'analysis/rmd/')
knitr::opts_chunk$set(fig.retina = 3, fig.align = 'center', fig.width = 6.93, 
                      fig.height = 6.13, out.width = "100%")
source(here::here("code/99-packages.R"))

@@

```{r}
records %<>% split(records[[2]]$beginposition)
